\section*{Database Requirements}

Our database will be on the role playing video game Skyrim. As with many role playing games, there exists a large amount of items, actors, locations, and quests. Many of these, by the nature of the type of game, are related to each other and can be modeled nicely by a database. For example, a monster can be of a certain type and multiples of those monsters can be found in a certain location. There also exists the notion of ownership within the game to be able to differentiate two of the exact same entities apart. An example of this ownership would be in the case of summoned monsters, which is directly tied to the actor that summoned it.


The goal is to model these types of relationships that are found within the game and implement them into our database. The main entities that will be within the database are as follow and are described further below: Characters, Weapons, Monsters, Monster-Type, Locations, Summoned Monsters, Boss Monsters, and Unique Items.

\subsection*{Entities}
\paragraph{Characters}
A character can be found in a certain Location and potentially in several Locations. All characters must be of a single race from the ten possible races that are found within the game’s characters. Some characters are essential and cannot be killed, while other characters are not. Some characters are friendly to the player while others will automatically be aggressive. 

\paragraph{Weapons}
There are different kinds of weapons that can be used within Skyrim. There are four general types that a weapon might be: one-handed, two-handed, archery, or staves. Each of the general types is composed of more specific types of weapons, for example daggers are found within the one-handed type and nowhere else. Weapons have an ID, a weight, a value, a damage value.

\paragraph{Monsters}
There are many different kinds of monsters that can be found within Skyrim, some quick examples are bears, wolves, and dragons. Certain monsters can be found in many locations. All monsters have a name, id, and level.  All monsters drop loot with an overall value that is based off of the level of the monster. Monsters deal a certain amount of damage to players and also have weaknesses and resistances to certain forms of damage. 

\paragraph{Locations}
Locations can of different types – either a city, dungeon, guild, or a miscellaneous location. Some locations are large and can have multiple locations within them, but some don’t. Cities must have a single ruler. Dungeons can have many different monsters within them.

\Large UNFINISHED
